\chapter{Widgets}

Members of the site need a landing page of sorts. A review link at the top of
the page isn't engaging enough. They need to have a feel for the content
they've created or collected. They also should be presented with options about
where to go from where they are now.

My first thought was to use \texttt{my.vocabulink.com}. But is it necessary to
create a separate page? Why not use the front page? The appeal of
\texttt{my.vocabulink.com} instead of \texttt{vocabulink.com/my/} is that it's
easier to remember and type. But isn't \texttt{vocabulink.com} or
\texttt{www.vocabulink.com} even easier? (Or in some cases, a web search for
``vocabulink''?)

So why not repurpose the front page as the member's home page when they're
logged in? Allow members to customize the page to fit what they want to keep
track of. To do so, we can use the concept of ``widgets''. A member can pick
from a collection of widgets and arrange them on their page. For a good
example, we can look at \href{http://www.google.com/ig}{iGoogle}.

New members receive a default arrangement of widgets so that they don't need
to learn how to customize their page until they're ready. Non-members do not
need a static front page. Instead, they can be considered a special case. We
can log in as the anonymous member and create their page for them.

\section{Default Arrangement}

\subsection{My Links}

The ``My Links'' widget helps keep the links that a member is reviewing
somewhere visible. It's important that they feel comforted by the ready
presence of their links instead of thinking about them being ``out there''
managed by the review algorithm.

The goal of the widget is to display only their $n$ latest links and to provide
a link to a link management page.
